---
title: "HW5"
output: github_document
---

```{r}
library(tidyverse)
library(rvest)
library(data.table)
library(purrr)
```

## Problem 1

```{r}
homicide_df = 
  read_csv("./homicide-data.csv", na = c("", "Unknown")) %>% #change " " and "unknown" to N/A
  mutate(city_state = str_c(city, state),
         resolution = case_when(
           disposition == "Closed without arrest" ~ "unsolved",
           disposition == "Open/No arrest" ~ "unsolved",
           disposition == "Closed by arrest" ~ "solved"
         )) %>% #combine city and state 2 col into 1 col #create a single outcome
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")
#put "homicide_df %>% count(disposition)" in console to get the number of different disposition
```

focus on Baltimore, MD.

```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "BaltimoreMD")

baltimore_summary = 
baltimore_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

baltimore_test = 
  prop.test(
  x = baltimore_summary %>% pull(unsolved),
  n = baltimore_summary %>% pull(n))

baltimore_test %>% 
  broom::tidy()#organize it as a data frame.
```

try to iterate across cities

first off, write a function and test it

```{r}
prop_test_function = function(city_df){
  
  city_summary = 
    city_df %>% 
    summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )
  
city_test = 
  prop.test(
    x = city_summary %>% pull(unsolved),
    n = city_summary %>% pull(n))

return(city_test)

}

prop_test_function(baltimore_df)

homicide_df %>% 
  filter(city_state == "AlbuquerqueNM") %>%
  prop_test_function()
```

let's iterate across all cities.

```{r}
results_df = 
  homicide_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_function),#run prop_test_function in each data list
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))

```

try to make a plot showing estimates and ci

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% #keep it in a right order
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

```{r}
homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  ) %>% 
  mutate(
    test_results = map2(unsolved, n, prop.test),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```

## Problem 2

```{r message=FALSE}
longitudinal_df = 
  tibble(
  filename = list.files(path = "data", pattern = "*.csv", full.names = TRUE),
  df = map(.x = filename, ~read_csv(.x))
) %>% 
  separate(filename, into = c("file", "name"), sep = "/") %>% 
  separate(name, into = c("arm", "id", "csv")) %>% 
  select(-file, -csv) %>% 
  unnest(df) %>% 
  mutate(arm = as.factor(arm)) %>% 
  pivot_longer(
    week_1 : week_8,
    names_to = "time_week",
    names_prefix = "week_",
    values_to = "observations"
  )
longitudinal_df
```

```{r}
longitudinal_df %>% 
  mutate(fullname = str_c(arm, id, sep = "_")) %>% 
ggplot(aes(x = time_week, y = observations, color = arm)) +
  geom_point() +
  geom_line(aes(group = fullname)) +
  labs(title = "Observations on each subject over time",
       x = "Week",
       y = "Observation") +
  theme(legend.position = "bottom")
```

**From the spaghetti plot we can learn that participants in control group have steady observations while participants in experimental group have increasing observations. According to this, we can initially guess that the experimental arm will lead to a higher obsevation.**

## Problem 3

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species)) 
```

Fill in missing values with the mean of non-missing values For character variables, fill in missing values with `virginica`
```{r}
iris_na = function(x) {
  if (is.numeric(x)){
    x[is.na(x)] = round(mean(x,na.rm = T))
  return(x)
  }
  if (is.character(x)) {
    x[is.na(x)] = "virginica"
    return(x)
  }}
iris_df = map_df(iris_with_missing, iris_na)
iris_df
```

